---
title: "lab-07-simpsons.Rmd"
author: "Maram Nawaf"
date: "17 March 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r load_libraries, message=FALSE}
library(tidyverse) 
library(mosaicData)
```


## Exercises


1.  
```{r whickam}
View(Whickham)
```
    
Your answer:
Observational , because we just watching the people and write the notes also we didn't involving in any situation or controlling any variables .
2.  
```{r observations}
nrow(Whickham)
```

Your answer;
1314 , represent recorded participants' age , smoking status at baseline 
3.  

```{r number_variables}
names(Whickham)
```

Your answer:  
3 , age (Numerical) , smoker and outcome are categorical 
```{r var_type}
unique(Whickham$outcome)
unique(Whickham$smoker)
unique(Whickham$age)
```

Your answer: using the 'unique()' function on the 3 variables we cloud see that "outcome" only takes alive or dead value, which makes it categorical non-ordinal.
"smoker" only takes yes or no, which also makes it categorical non-ordinal.
age is numerical continous data.
continous one of the best ways to visualise categorical data is through the use ofbar charts.

```{r plot_outcome}
ggplot(Whickham, aes(x = outcome)) +
  geom_bar()
```


```{r plot_smoker}
ggplot(Whickham, aes(x = smoker)) +
  geom_bar()
```

```{r plot_age}
ggplot(Whickham, aes(x = age)) +
  geom_bar()
```


4. Whickham %>%
  count(smoker, outcome)
 502+230
 230/732

```{r plot_smokeVSincome_1}
ggplot(data=Whickham, aes(x=smoker, y=outcome, color=outcome)) + geom_bar(stat="identity")
```

Knit, commit, and push to github.

5.The number of deaths of smokers was lower than that of non-smokers 

```{r plot_smokeVSincome_2}
Whickham %>%
  count(smoker, outcome)
502+230
230/732
```

6.

```{r age_cat}
Whickham <- Whickham%>% mutate (age_cat = case_when (age <= 44 ~ "18-44", age > 44. & age <= 64 ~ "45-64", age > 64 ~ "65+"))
```

7. 

```{r plot_smokeVSincome_3}
ggplot(data=Whickham, aes(x=outcome, y=smoker,color=smoker, fill=age_cat)) + geom_bar(stat="identity") +facet_wrap(~age_cat)
```

Knit, commit, and push to github.