---
title: "lab-07-simpsons.Rmd"
author: "Maram Nawaf"
date: "17 March 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r load_libraries, message=FALSE}
library(tidyverse) 
library(mosaicData)
```


## Exercises


1.  
```{r whickam}

```
    
Your answer:
Observational , because we just watching the people and write the notes also we didn't involving in any situation or controlling any variables .
2.  
```{r observations}
nrow(Whickham)
```

Your answer;
1314 , represent recorded participants' age , smoking status at baseline 
3.  

```{r number_variables}
names(Whickham)
```

Your answer:  
3 , age (Numerical) , smoker and outcome are categorical 
```{r var_type}
unique(Whickham$outcome)
unique(Whickham$smoker)
unique(Whickham$age)
```

Your answer: using the 'unique()' function on the 3 variables we cloud see that "outcome" only takes alive or dead value, which makes it categorical non-ordinal.
"smoker" only takes yes or no, which also makes it categorical non-ordinal.
age is numerical continous data.
continous one of the best ways to visualise categorical data is through the use ofbar charts.

```{r plot_outcome}
ggplot(Whickham, aes(x = outcome)) +
  geom_bar()
```


```{r plot_smoker}
ggplot(Whickham, aes(x = smoker)) +
  geom_bar()
```

```{r plot_age}
ggplot(Whickham, aes(x = age)) +
  geom_bar()
```


4. 

```{r plot_smokeVSincome_1}

```

Knit, commit, and push to github.

5. 

```{r plot_smokeVSincome_2}
Whickham %>%
  count(smoker, outcome)
```

6.

```{r age_cat}

```

7. 

```{r plot_smokeVSincome_3}

```

Knit, commit, and push to github.